---
title: "Are power forwards and centers adapting to Small Ball?"
author: "Derek Corcoran"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: yes
---

It is no secret that in the last few years the media, basketball players, and ex-basketball players have been talking about small ball revolution. As we can see bellow search interest (If we don't take into account a moment in 2006) has been going up consistently.

Most of times, the small ball line-ups tend to slide a small froward to the power froward position (think Kevin Durant in OKC or Lebron James in Cleveland), or slide a Power Froward to the Center Position (A la Draymond Green in GSW). 

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(ggthemr)
library(gtrendsR)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, fig.cap="Search of Small ball According to Google Trends"}
gconnect("derek.corcoran.barrios@gmail.com", "duo5241K+") 
lang_trend <- gtrends(c("small ball"))
trend <- lang_trend$trend
plot(lang_trend)
```

We keep hearing how NBA players say the will add the three point shot to their repertoir during the off-season, if that was the case we could start seeing more three point shooting power frowards like Dirk Nowitzki or Kevin love in pace and space line-ups that don't sacrifice defensive rebounding, height or rim protection, but are Power Frowards adapting to their new reality? We will analize the data of three point shooting from season 97-98 to now to see the answer.

```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
library(SportsAnalytics)
NBA15_16 <- fetch_NBAPlayerStatistics(season = "15-16", what = c("", ".Home", ".Away"))
NBA15_16$Three_pct <- NBA15_16$ThreesMade/NBA15_16$ThreesAttempted
NBA15_16$Year <- 2016
NBA15_16$Mean3p <- mean(NBA15_16$Three_pct, na.rm= TRUE)
NBA15_16$Avobe_Av <- NBA15_16$Three_pct > NBA15_16$Mean3p

NBA14_15 <- fetch_NBAPlayerStatistics(season = "14-15", what = c("", ".Home", ".Away"))
NBA14_15$Three_pct <- NBA14_15$ThreesMade/NBA14_15$ThreesAttempted
NBA14_15$Year <- 2015
NBA14_15$Mean3p <- mean(NBA14_15$Three_pct, na.rm= TRUE)
NBA14_15$Avobe_Av <- NBA14_15$Three_pct > NBA14_15$Mean3p

NBA13_14 <- fetch_NBAPlayerStatistics(season = "13-14", what = c("", ".Home", ".Away"))
NBA13_14$Three_pct <- NBA13_14$ThreesMade/NBA13_14$ThreesAttempted
NBA13_14$Year <- 2014
NBA13_14$Mean3p <- mean(NBA13_14$Three_pct, na.rm= TRUE)
NBA13_14$Avobe_Av <- NBA13_14$Three_pct > NBA13_14$Mean3p

NBA12_13 <- fetch_NBAPlayerStatistics(season = "12-13", what = c("", ".Home", ".Away"))
NBA12_13$Three_pct <- NBA12_13$ThreesMade/NBA12_13$ThreesAttempted
NBA12_13$Year <- 2013
NBA12_13$Mean3p <- mean(NBA12_13$Three_pct, na.rm= TRUE)
NBA12_13$Avobe_Av <- NBA12_13$Three_pct > NBA12_13$Mean3p

NBA11_12 <- fetch_NBAPlayerStatistics(season = "11-12", what = c("", ".Home", ".Away"))
NBA11_12$Three_pct <- NBA11_12$ThreesMade/NBA11_12$ThreesAttempted
NBA11_12$Year <- 2012
NBA11_12$Mean3p <- mean(NBA11_12$Three_pct, na.rm= TRUE)
NBA11_12$Avobe_Av <- NBA11_12$Three_pct > NBA11_12$Mean3p

NBA10_11 <- fetch_NBAPlayerStatistics(season = "10-11", what = c("", ".Home", ".Away"))
NBA10_11$Three_pct <- NBA10_11$ThreesMade/NBA10_11$ThreesAttempted
NBA10_11$Year <- 2011
NBA10_11$Mean3p <- mean(NBA10_11$Three_pct, na.rm= TRUE)
NBA10_11$Avobe_Av <- NBA10_11$Three_pct > NBA10_11$Mean3p

NBA09_10 <- fetch_NBAPlayerStatistics(season = "09-10", what = c("", ".Home", ".Away"))
NBA09_10$Three_pct <- NBA09_10$ThreesMade/NBA09_10$ThreesAttempted
NBA09_10$Year <- 2010
NBA09_10$Mean3p <- mean(NBA09_10$Three_pct, na.rm= TRUE)
NBA09_10$Avobe_Av <- NBA09_10$Three_pct > NBA09_10$Mean3p

NBA08_09 <- fetch_NBAPlayerStatistics(season = "08-09", what = c("", ".Home", ".Away"))
NBA08_09$Three_pct <- NBA08_09$ThreesMade/NBA08_09$ThreesAttempted
NBA08_09$Year <- 2009
NBA08_09$Mean3p <- mean(NBA08_09$Three_pct, na.rm= TRUE)
NBA08_09$Avobe_Av <- NBA08_09$Three_pct > NBA08_09$Mean3p

NBA07_08 <- fetch_NBAPlayerStatistics(season = "07-08", what = c("", ".Home", ".Away"))
NBA07_08$Three_pct <- NBA07_08$ThreesMade/NBA07_08$ThreesAttempted
NBA07_08$Year <- 2008
NBA07_08$Mean3p <- mean(NBA07_08$Three_pct, na.rm= TRUE)
NBA07_08$Avobe_Av <- NBA07_08$Three_pct > NBA07_08$Mean3p

NBA06_07 <- fetch_NBAPlayerStatistics(season = "06-07", what = c("", ".Home", ".Away"))
NBA06_07$Three_pct <- NBA06_07$ThreesMade/NBA06_07$ThreesAttempted
NBA06_07$Year <- 2007
NBA06_07$Mean3p <- mean(NBA06_07$Three_pct, na.rm= TRUE)
NBA06_07$Avobe_Av <- NBA06_07$Three_pct > NBA06_07$Mean3p

NBA05_06 <- fetch_NBAPlayerStatistics(season = "05-06", what = c("", ".Home", ".Away"))
NBA05_06$Three_pct <- NBA05_06$ThreesMade/NBA05_06$ThreesAttempted
NBA05_06$Year <- 2006
NBA05_06$Mean3p <- mean(NBA05_06$Three_pct, na.rm= TRUE)
NBA05_06$Avobe_Av <- NBA05_06$Three_pct > NBA05_06$Mean3p

NBA04_05 <- fetch_NBAPlayerStatistics(season = "04-05", what = c("", ".Home", ".Away"))
NBA04_05$Three_pct <- NBA04_05$ThreesMade/NBA04_05$ThreesAttempted
NBA04_05$Year <- 2005
NBA04_05$Mean3p <- mean(NBA04_05$Three_pct, na.rm= TRUE)
NBA04_05$Avobe_Av <- NBA04_05$Three_pct > NBA04_05$Mean3p

NBA03_04 <- fetch_NBAPlayerStatistics(season = "03-04", what = c("", ".Home", ".Away"))
NBA03_04$Three_pct <- NBA03_04$ThreesMade/NBA03_04$ThreesAttempted
NBA03_04$Year <- 2004
NBA03_04$Mean3p <- mean(NBA03_04$Three_pct, na.rm= TRUE)
NBA03_04$Avobe_Av <- NBA03_04$Three_pct > NBA03_04$Mean3p

NBA02_03 <- fetch_NBAPlayerStatistics(season = "02-03", what = c("", ".Home", ".Away"))
NBA02_03$Three_pct <- NBA02_03$ThreesMade/NBA02_03$ThreesAttempted
NBA02_03$Year <- 2003
NBA02_03$Mean3p <- mean(NBA02_03$Three_pct, na.rm= TRUE)
NBA02_03$Avobe_Av <- NBA02_03$Three_pct > NBA02_03$Mean3p

NBA01_02 <- fetch_NBAPlayerStatistics(season = "01-02", what = c("", ".Home", ".Away"))
NBA01_02$Three_pct <- NBA01_02$ThreesMade/NBA01_02$ThreesAttempted
NBA01_02$Year <- 2002
NBA01_02$Mean3p <- mean(NBA01_02$Three_pct, na.rm= TRUE)
NBA01_02$Avobe_Av <- NBA01_02$Three_pct > NBA01_02$Mean3p

NBA00_01 <- fetch_NBAPlayerStatistics(season = "00-01", what = c("", ".Home", ".Away"))
NBA00_01$Three_pct <- NBA00_01$ThreesMade/NBA00_01$ThreesAttempted
NBA00_01$Year <- 2001
NBA00_01$Mean3p <- mean(NBA00_01$Three_pct, na.rm= TRUE)
NBA00_01$Avobe_Av <- NBA00_01$Three_pct > NBA00_01$Mean3p

NBA99_00 <- fetch_NBAPlayerStatistics(season = "99-00", what = c("", ".Home", ".Away"))
NBA99_00$Three_pct <- NBA99_00$ThreesMade/NBA99_00$ThreesAttempted
NBA99_00$Year <- 2000
NBA99_00$Mean3p <- mean(NBA99_00$Three_pct, na.rm= TRUE)
NBA99_00$Avobe_Av <- NBA99_00$Three_pct > NBA99_00$Mean3p

NBA98_99 <- fetch_NBAPlayerStatistics(season = "98-99", what = c("", ".Home", ".Away"))
NBA98_99$Three_pct <- NBA98_99$ThreesMade/NBA98_99$ThreesAttempted
NBA98_99$Year <- 1999
NBA98_99$Mean3p <- mean(NBA98_99$Three_pct, na.rm= TRUE)
NBA98_99$Avobe_Av <- NBA98_99$Three_pct > NBA98_99$Mean3p

NBA97_98 <- fetch_NBAPlayerStatistics(season = "97-98", what = c("", ".Home", ".Away"))
NBA97_98$Three_pct <- NBA97_98$ThreesMade/NBA97_98$ThreesAttempted
NBA97_98$Year <- 1998
NBA97_98$Mean3p <- mean(NBA98_99$Three_pct, na.rm= TRUE)
NBA97_98$Avobe_Av <- NBA97_98$Three_pct > NBA97_98$Mean3p


NBA <- rbind (NBA15_16, NBA14_15, NBA13_14, NBA12_13, NBA11_12, NBA10_11, NBA09_10, NBA07_08 , NBA08_09, NBA06_07, NBA05_06, NBA04_05,  NBA03_04, NBA02_03, NBA01_02, NBA00_01, NBA99_00, NBA98_99, NBA97_98)
NBA2 <- NBA
NBA2$Position <- as.factor("All")

NBA<- rbind(NBA2, NBA)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, fig.cap="Percentage of players by position shooting above average 3 point shooting percentage"}

library(dplyr)

#NBA <- filter(NBA, ThreesAttempted > 10)

NBA_Year_Position <- group_by(NBA, Year, Position)

NBA_Year_Position<- summarise(NBA_Year_Position, Mean = mean(Three_pct, na.rm = TRUE), SD = sd(Three_pct, na.rm = TRUE), n = n(), above = sum(Avobe_Av, na.rm = TRUE))
NBA_Year_Position <- filter(NBA_Year_Position, Position != "NA")
NBA_Year_Position$pct <- NBA_Year_Position$above/NBA_Year_Position$n

library(ggplot2)
ggthemr("earth", type="outer", layout="scientific", spacing=2)
four <- ggplot(data = NBA_Year_Position, aes(x = Year, y = pct)) + geom_point(aes(color = Position)) + geom_smooth(method = "lm",aes(color=Position))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}

NBA<- filter(NBA, Position != "NA")
NBA<- filter(NBA, Three_pct != "NaN")
```

#Results
##Three point percentage per position
As we see in figure 2 we see that every position has improved the 3 pt percentage in the last 18 years in the NBA. It seems that Small Frowards, Power Frowards, and Centers have improved a lot more than guards, but guards keep having a higher 3 point percentage than frowards and Centers. According to the GML (Table 1) Small Frowards are the ones having a higher than average three point shooting, also looking at the points in figure 1, we can see that Small Frowards have averaged more than 33% in three point shots on the last 2 years, which is the threshold of the three point shot equaling the value of a 50% two pointer.

```{r, echo=FALSE, cache=TRUE, fig.cap= "Three point percentage trends from 1998 to 2016 by position, the red horizontal line shows the 33% threshold of the three point shot equaling the value of a 50% two pointer"}
ggthemr("earth", type="outer", layout="scientific", spacing=2)

ggplot(data = NBA_Year_Position, aes(x = Year, y = Mean)) + stat_smooth(method="lm", aes(color = Position)) + ylab("3-Point Shooting %") + geom_hline(aes(yintercept= 0.33))+ geom_point(aes(color = Position), alpha = 0.5)
#ggplot(data = NBA, aes(x = Year, y = Three_pct)) + geom_smooth(aes(weight=TotalMinutesPlayed,color=Position))

```

```{r,r, echo=FALSE, cache=TRUE, results="asis"}
library(stargazer)
stargazer(glm(Mean ~ Year + Position, data = NBA_Year_Position), title = "Glm terms and their p-values")

```

##Percentage of players by position with above average three point shooting percentage

We also see an increace of the percentage of players by position that are above average three point shooters, as we see in Figure 3, small Frowards, Power Frowards and Center have increased the percentage of players that are avobe average three point shooters, put still only Shoting Guards, Small Frowards and Point Guards are the only ones with over 50% of players with above average shooting.


##Percentage of players by position in the top 40 of 3 point shooting percentage

Finally when we analize the percentage of players per position in elite of 3 point shooters we see that in that regard the percentage of elite shooters among centers and Power Frowards has not increased in the last 18 years, whereas Small Frowards and Point Guards have (Figure 4)

```{r, echo= FALSE, cache= FALSE, fig.cap="Percentage of players by position, above that year 3 point shooting percentage average"}
library(ggplot2)
ggthemr("earth", type="outer", layout="scientific", spacing=2)

four
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

library(dplyr)
library(knitr)
NBA <- filter(NBA, ThreesMade >= 34)
NBA <- filter(NBA, ThreesMade >= 45 | Year == "1999")
NBA <- filter(NBA, ThreesMade >= 82 | Year == "1999" | Year == "2012")

rank <- arrange(NBA, Year, desc(Three_pct))
rank <- filter(rank, Position != "All")
rank$Position <- factor(rank$Position)
rank <- rank[,-c(1,3,5:25,28,29)]

require(data.table)
d <- data.table(rank, key="Year")
rank <- d[, head(.SD, 40), by=Year]
```

```{r, echo = FALSE, fig.cap= "Percentage of players by position in the top 40 of NBA 3 point shooting percentage"}
rank<-data.frame(rank)
rank<- (table(rank[,c(1,3)]))
ggthemr("earth", type="outer", layout="scientific", spacing=2)

rank <- data.frame(rank)
rank$pct <- rank$Freq/40
rank$Year <- as.numeric(as.character(rank$Year))
rank <- filter(rank, Position != "All")
ggplot(rank, aes(x = Year, y = pct)) + geom_point(aes(colour = Position)) + geom_smooth(method = "lm",aes(color=Position))
```